CDI:WS Production Bias Report

### 2021-08-25 ws_prod_report.Rmd
added some notes

```{r, sex-table}
#d_demo <- d_demo %>% mutate(relevel() # remove empty "Other" level?
d_demo <- d_demo %>% 
  filter(comprehension!=0, !is.na(sex)) %>% # can't fit children not producing words, or with NA sex in group model
  arrange(data_id) %>%
  mutate(eth_group = ifelse(ethnicity=="White", "White", "Nonwhite"),
         ses_group = 
           ifelse(is.element(mom_ed, c("None", "Primary", "Some Secondary", "Secondary")), "low", "high"))

@@

### Removing Biased Items
Histogram of Sex Items from GLIMMER
```{r, fig.width=3, fig.height=3, echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
mm_sex <- extract_group_df(mod_intuitive_sex, groups=c("Male","Female"))
sex_hist <- item_difficulty_difference_histogram(mm_sex)

orig_sex <- get_extreme_item_difficulty_differences(mm_sex, 2.25) # min: -.53 max: 1.06 (mean + 2SD) mean: .265
sex_hist
```

@@

```{r, eval=F}
d_demo <- d_demo %>% 
  filter(comprehension!=0, !is.na(sex)) %>% # can't fit children not producing words, or with NA sex in group model
  arrange(data_id) %>%
  mutate(eth_group = ifelse(ethnicity=="White", "White", "Nonwhite"),
         ses_group = 
           ifelse(is.element(mom_ed, c("None", "Primary", "Some Secondary", "Secondary")), "low", "high"))

@@

Histogram from SES GLIMMER
```{r, fig.width=3, fig.height=3, echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
#used this to find out the that the two groups are 0 1 not high low, not sure why
#groups <- c("0","1")
#group_model <- mod_intuitive_ses
#Mit = as_tibble(coef(group_model, simplify=T)[[groups[1]]]$items) %>%
#    mutate(definition = rownames(coef(group_model, simplify=T)[[groups[1]]]$items),
#           group1 = groups[1],
#          group2 = groups[2])

@@

```{r, eval=F}
#do we need to have removed NA sex kids for the ses model
d_demo <- d_demo %>% 
  filter(comprehension!=0, !is.na(sex)) %>% # can't fit children not producing words, or with NA sex in group model
  arrange(data_id) %>%
  mutate(eth_group = ifelse(ethnicity=="White", "White", "Nonwhite"),
         ses_group = 
           ifelse(is.element(mom_ed, c("None", "Primary", "Some Secondary", "Secondary")), "low", "high"))

>>>>

```{r, sex-table}
#d_demo <- d_demo %>% mutate(relevel() # remove empty "Other" level?
#need this so that d_demo extists in the right form with you knit.
d_demo <- d_demo %>% 
  filter(comprehension!=0, !is.na(sex)) %>% # can't fit children not producing words, or with NA sex in group model
  arrange(data_id) %>%
  mutate(eth_group = ifelse(ethnicity=="White", "White", "Nonwhite"),
         ses_group = 
           ifelse(is.element(mom_ed, c("None", "Primary", "Some Secondary", "Secondary")), "low", "high"))

@@

### Removing Biased Items
Histogram of Sex Items from GLIMMER
```{r, fig.width=3, fig.height=3, echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
mm_sex <- extract_group_df(mod_intuitive_sex, groups=c("Male","Female"))
sex_hist <- item_difficulty_difference_histogram(mm_sex)
#added the option to change SD threshold
orig_sex <- get_extreme_item_difficulty_differences(mm_sex, 2.25) # min: -.53 max: 1.06 (mean + 2SD) mean: .265
sex_hist
```

@@

```{r, eval=F}
#may no longer be nesesary now that its up top and I have already fit the models but I left it for now. 
d_demo <- d_demo %>% 
  filter(comprehension!=0, !is.na(sex)) %>% # can't fit children not producing words, or with NA sex in group model
  arrange(data_id) %>%
  mutate(eth_group = ifelse(ethnicity=="White", "White", "Nonwhite"),
         ses_group = 
           ifelse(is.element(mom_ed, c("None", "Primary", "Some Secondary", "Secondary")), "low", "high"))

@@

Histogram from SES GLIMMER
```{r, fig.width=3, fig.height=3, echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
#used this to find out the that the two groups are 0 1 not high low, not sure why
#groups <- c("0","1")
#group_model <- mod_intuitive_ses
#Mit = as_tibble(coef(group_model, simplify=T)[[groups[1]]]$items) %>%

@@

```{r, eval=F}
#do we need to have removed NA sex kids for the ses model?
d_demo <- d_demo %>% 
  filter(comprehension!=0, !is.na(sex)) %>% # can't fit children not producing words, or with NA sex in group model
  arrange(data_id) %>%
  mutate(eth_group = ifelse(ethnicity=="White", "White", "Nonwhite"),
         ses_group = 
           ifelse(is.element(mom_ed, c("None", "Primary", "Some Secondary", "Secondary")), "low", "high"))
